Gravitational disturbance

### 2017-03-10 manuscript/manuscript.tex
new references
include the reference of Forsberg 1984 and the term density anomalies

@@

Traditionally, the Earth's gravity field is approximated 
by the gravity field produced by a geocentric and rigid ellipsoid 
of revolution which has the minor axis $b$ 
coincident with the mean rotating axis of the Earth $Z$, the 
same total mass (including the atmosphere) and also the
same angular velocity of the Earth (Figure \ref{fig:fig1}).
Another characteristic of this model is that its
limiting surface coincides with a particular equipotential 
of its own gravity field.
This model is called as normal Earth and its gravity
field is called normal gravity field
\citep{vanicek1987, hofmann-wellenhof-moritz2005, torge2014}.

@@

It seems logical to expected that the gravitational disturbance 
is caused by contrasts between the actual internal 
density distribution of the Earth and the internal density 
distribution of the normal Earth.
In applied geophysics, these density differences are generally 
called ``anomalous masses" (e.g., \citeauthor{hammer1945}, 
\citeyear{hammer1945}; \citeauthor{lafehr1965}, \citeyear{lafehr1965})
or ``gravity sources" (e.g., \citeauthor{blakely1996}, 
\citeyear{blakely1996}). Here, we opted for using the second term.

>>>>

URGENTE: \citep{marussi1974}, \citep{torge2012}, section 4.2.1

@@

Traditionally, the Earth's gravity field is approximated 
by the gravity field produced by a geocentric and rigid ellipsoid 
of revolution which has the minor axis $b$ 
coincident with the mean rotating axis of the Earth $Z$, the 
same total mass (including the atmosphere) and also the
same angular velocity of the Earth (Figure \ref{fig:fig1}).
Another characteristic of this model is that its
limiting surface coincides with a particular equipotential 
of its own gravity field.
This model is called as normal Earth and its gravity
field is called normal gravity field
\citep{vanicek1987, hofmann-wellenhof-moritz2005, torge2012}.

@@

It seems logical to expected that the gravitational disturbance 
is caused by contrasts between the actual internal 
density distribution of the Earth and the internal density 
distribution of the normal Earth.
In applied geophysics, these density differences are generally 
called ``anomalous masses" (e.g., \citeauthor{hammer1945}, 
\citeyear{hammer1945}; \citeauthor{lafehr1965}, \citeyear{lafehr1965}),
``density anomalies" (e.g., \citeauthor{forsberg1984}, \citeyear{forsberg1984})
or ``gravity sources" (e.g., \citeauthor{blakely1996}, 
\citeyear{blakely1996}). Here, we opted for using the last term.
